Capstone Movielens Report

### 2025-12-21 reports/capstone-movielens.site/02.5.UME-model.Rmd
Fix for the `XXXX Model Regularization: Fine-tuning` sections of the report.

UM_effect.loop_starter <- c(endpoints["start"], 
                            endpoints["end"], 
                            8)
```
```{r}
UM_effect.loop_starter
```

@@

Below are the results of fine-tuning the *UMGYE Model*:

>>>>

UM_effect.loop_starter <- c(endpoints["start"], 
                            endpoints["end"], 
                            8)
```
```{r, echo=FALSE}
writeLines("*** Values of the endpoints and the divisor for the interval of `lambda` values ***")
```
```{r}
UM_effect.loop_starter
```

@@

Below are the results of fine-tuning the *UME Model*:

### 2025-12-21 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Fix for the `XXXX Model Regularization: Fine-tuning` sections of the report.

UMG_effect.loop_starter <- c(endpoints["start"], 
                            endpoints["end"], 
                            8)
```
```{r}
UMG_effect.loop_starter
```

@@

Below are the results of fine-tuning the *UMGYE Model*:

>>>>

UMG_effect.loop_starter <- c(endpoints["start"], 
                            endpoints["end"], 
                            8)
```
```{r, echo=FALSE}
writeLines("*** Values of the endpoints and the divisor for the interval of `lambda` values ***")
```
```{r}
UMG_effect.loop_starter
```

@@

Below are the results of fine-tuning the *UMGE Model*:

### 2025-12-21 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Fix for the `XXXX Model Regularization: Fine-tuning` sections of the report.

UMGYE.loop_starter <- c(endpoints["start"], 
                        endpoints["end"], 
                        8)
```
```{r}
UMGYE.loop_starter
```

>>>>

UMGYE.loop_starter <- c(endpoints["start"], 
                        endpoints["end"], 
                        8)
```
```{r, echo=FALSE}
writeLines("*** Values of the endpoints and the divisor for the interval of `lambda` values ***")
```
```{r}
UMGYE.loop_starter
```

### 2025-12-21 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Fix for the `XXXX Model Regularization: Fine-tuning` sections of the report.

UMGYDE.loop_starter <- c(endpoints["start"], 
                        endpoints["end"], 
                        8)
```
```{r}
UMGYDE.loop_starter
```

>>>>

UMGYDE.loop_starter <- c(endpoints["start"], 
                        endpoints["end"], 
                        8)
```
```{r, echo=FALSE}
writeLines("*** Values of the endpoints and the divisor for the interval of `lambda` values ***")
```
```{r}
UMGYDE.loop_starter
```
